---
title: "204 Homework 2"
author: "Taylor Lockmann"
date: "4/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
```
# Part 1: Marginal abatement costs

Note: For this analysis, the following terms are used synonymously:
x = Q
y = P

## Read in the data & exploratory viz

```{r}
# Read in the data

water_data <- read_csv(here("data", "HW2_Water.csv")) %>% 
  clean_names()
#View(water_data)

# Exploratory visualization

ggplot(data = water_data, aes(x = reduced_water_use_abatement, y = mc_agriculture))+
  geom_point()+
  theme_bw()
```

## Start building regression model

Once we find the coefficients from these linear regression models, we can use them to write estimated Marginal Cost curve equations using the format $$MC = a + bA$$
Where MC = Marginal Cost, a = y-intercept coefficient, b = slope coefficient, and A = Abatement level.

```{r}
# Start building regression model

lm_ag <- lm(formula = mc_agriculture ~ reduced_water_use_abatement, data = water_data)

summary(lm_ag)
#coefficients(lm_ag)

# From this linear regression model we can see that our y-intercept = 1.93603, and slope = 0.51035. We can now add this line to our current plot. 

ag_function <- function(x) 0.51035*x + 1.93603
```

## Repeat for all other sectors

```{r}
## Meat

lm_meat <- lm(formula = mc_meat ~ reduced_water_use_abatement, data = water_data)

coefficients(lm_meat)

meat_function <- function(x) 0.37534*x + 9.4808

## Industrial

lm_industrial <- lm(formula = mc_industrial ~ reduced_water_use_abatement, data = water_data)

coefficients(lm_industrial)

industrial_function <- function(x) 1.13009*x - 26.80662

## Urban

lm_urban <- lm(formula = mc_urban ~ reduced_water_use_abatement, data = water_data)

coefficients(lm_urban)

urban_function <- function(x) 0.59713*x - 13.82868
```

## Now graph all the functions together

```{r}

ggplot(data = water_data, aes(x = reduced_water_use_abatement))+
  stat_function(fun = ag_function,
                color = "red")+
  stat_function(fun = industrial_function,
                color = "blue")+
  stat_function(fun = meat_function,
                color = "forestgreen")+
  stat_function(fun = urban_function,
                color = "coral")+
  annotate("text", x = 40, y = 140, color = "red", label = "Agriculture: 0.51035*x + 1.93603")+
  annotate("text", x = 40, y = 130, color = "blue", label = "Industrial: 1.13009*x - 26.80662")+
  annotate("text", x = 40, y = 120, color = "forestgreen", label = "Meat: 0.37534*x + 9.4808")+
  annotate("text", x = 40, y = 110, color = "coral", label = "Urban: 0.59713*x - 13.82868")+
  theme_bw()+
  labs(
    y = "Marginal Cost of Abatement ($/AF)",
    x = "Reduction in Water Use (AF)",
    title = "Marginal Cost Curves"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0, 150)
  

```

# Part 2: Demand Curves

In the pollution-reduction space, the amount of pollution can be given by the equation: $$Q = \bar{Q} - A$$
Where Q = total amount of pollution, \bar{Q} = baseline pollution level, and A = Abatement.

By rearranging this equation and solving for A, we can then plug A into our equation for MC (above), and thus find that the demand curve equation is given by: $$P = a + b(\bar{Q} - Q)$$

Now let's do this for each of our sectors:

### Agriculture: current use = 170AF

P = 1.936 + 0.510(170-Q)
P = 88.696 - 0.510Q
```{r}
ag_demand <- function(x) 88.696 - 0.510*x
```

### Industrial: current use = 230AF

P = -26.807 + 1.13(230 - Q)
P = 233.093 - 1.13Q
```{r}
industrial_demand <- function(x) 233.093 - 1.13*x
```

### Meat: current use  = 200AF

P = 9.48 + 0.375(200 - Q)
P = 84.48 - 0.375Q
```{r}
meat_demand <- function(x) 84.48 - 0.375*x
```

### Urban: current use = 300AF

P = -13.83 + 0.597(300 - Q)
P = 165.27 - 0.597Q
```{r}
urban_demand <- function(x) 165.27 - 0.597*x
```


## Now plot all the demand curves together

```{r}
ggplot()+
  stat_function(fun = ag_demand,
                color = "red")+
  stat_function(fun = industrial_demand,
                color = "blue")+
  stat_function(fun = meat_demand,
                color = "forestgreen")+
  stat_function(fun = urban_demand,
                color = "coral")+
  annotate("text", x = 225, y = 225, color = "red", label = "Agriculture: P = 88.696 - 0.510Q")+
  annotate("text", x = 225, y = 210, color = "blue", label = "Industrial: P = 233.093 - 1.13Q")+
  annotate("text", x = 225, y = 195, color = "forestgreen", label = "Meat: P = 84.48 - 0.375Q")+
  annotate("text", x = 225, y = 180, color = "coral", label = "Urban: P = 165.27 - 0.597Q")+
  theme_bw()+
  labs(
    y = "Price ($)",
    x = "Water Use (AF)",
    title = "Demand Curves"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  xlim(0, 300)+
  ylim(0, 250)+
  theme(plot.title = element_text(hjust = 0.5))
```

# Part 3: Baja California Policy Options

### 3b)

Found the aggregate demand curve by solving for Q for each of the Ag, Meat, and Industrial sectors, then adding those three equations together. We end up with this:

```{r}
aggr_demand <- function(x) (x/-5.51) + 109.83
```


Make a graph of the three sectors, plus their aggregate demand curve
```{r}
ggplot()+
  stat_function(fun = ag_demand,
                color = "red")+
  stat_function(fun = industrial_demand,
                color = "blue")+
  stat_function(fun = meat_demand,
                color = "forestgreen")+
  stat_function(fun = aggr_demand,
                color = "purple",
                size = 2)+
  annotate("text", x = 400, y = 225, color = "red", label = "Agriculture: P = 88.696 - 0.510Q")+
  annotate("text", x = 400, y = 210, color = "blue", label = "Industrial: P = 233.093 - 1.13Q")+
  annotate("text", x = 400, y = 195, color = "forestgreen", label = "Meat: P = 84.48 - 0.375Q")+
  annotate("text", x = 400, y = 180, color = "purple", label = "Aggregate Demand: P = 109.83 - 0.181Q")+
  theme_bw()+
  labs(
    y = "Price ($)",
    x = "Water Use (AF)",
    title = "Demand Curves for Baja California"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  xlim(0, 600)+
  ylim(0, 250)+
  theme(plot.title = element_text(hjust = 0.5))
```

### 3c)
Found the aggregate marginal cost curve by solving for Q for each of the Ag, Meat, and Industrial sectors, then adding those three equations together. We end up with this:

```{r}
aggr_mc <- function(x) 0.18*x + 0.97
```

Make a graph of the three sectors, plus their aggregate marginal cost curve

```{r}
ggplot(data = water_data, aes(x = reduced_water_use_abatement))+
  stat_function(fun = ag_function,
                color = "red")+
  stat_function(fun = industrial_function,
                color = "blue")+
  stat_function(fun = meat_function,
                color = "forestgreen")+
  stat_function(fun = aggr_mc,
                color = "purple",
                size = 2)+
  annotate("text", x = 100, y = 140, color = "red", label = "Agriculture: 0.51035*x + 1.93603")+
  annotate("text", x = 100, y = 130, color = "blue", label = "Industrial: 1.13009*x - 26.80662")+
  annotate("text", x = 100, y = 120, color = "forestgreen", label = "Meat: 0.37534*x + 9.4808")+
  annotate("text", x = 100, y = 110, color = "purple", label = "Aggregate Marginal Cost: 0.18*x + 0.97")+
  theme_bw()+
  labs(
    y = "Marginal Cost of Abatement ($/AF)",
    x = "Reduction in Water Use (AF)",
    title = "Marginal Cost Curves in Baja California"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0, 150)+
  xlim(0, 350)
  
```

# Part 4: BCS & BC Cap and Trade Together

Solve each marginal cost curve for Q for all four sectors, add those equations together to get the aggregate demand curve for all four sectors.

```{r}
aggr_mc_foursectors <- function(x) 0.14*x - 2.48

# Now put all four of these sectors on the graph, plus the aggregate marginal cost curve of all four.

ggplot(data = water_data, aes(x = reduced_water_use_abatement))+
  stat_function(fun = ag_function,
                color = "red")+
  stat_function(fun = industrial_function,
                color = "blue")+
  stat_function(fun = meat_function,
                color = "forestgreen")+
  stat_function(fun = urban_function,
                color = "coral")+
  stat_function(fun = aggr_mc_foursectors,
                color = "purple",
                size = 2)+
  annotate("text", x = 75, y = 140, color = "red", label = "Agriculture: 0.51035*x + 1.93603")+
  annotate("text", x = 75, y = 130, color = "blue", label = "Industrial: 1.13009*x - 26.80662")+
  annotate("text", x = 75, y = 120, color = "forestgreen", label = "Meat: 0.37534*x + 9.4808")+
  annotate("text", x = 75, y = 110, color = "coral", label = "Urban: 0.59713*x - 13.82868")+
  annotate("text", x = 90, y = 100, color = "purple", label = "Agg MC Curve (4sectors): 0.14*x - 2.48")+
  theme_bw()+
  labs(
    y = "Marginal Cost of Abatement ($/AF)",
    x = "Reduction in Water Use (AF)",
    title = "Marginal Cost Curves (BC + BCS)"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0, 150)+
  xlim(0, 350)

```





# Part 5: Ecosystem services


```{r}
# Marginal Cost curve plus added $10 of ecosystem degradation at each AF.

aggr_mc_ecosystem <- function(x) 0.18*x + 0.97 + 10

# Now graph it

ggplot(data = water_data, aes(x = reduced_water_use_abatement))+
  stat_function(fun = ag_function,
                color = "red")+
  stat_function(fun = industrial_function,
                color = "blue")+
  stat_function(fun = meat_function,
                color = "forestgreen")+
  stat_function(fun = aggr_mc,
                color = "purple")+
  stat_function(fun = aggr_mc_ecosystem,
                color = "orange",
                size = 2)+
  annotate("text", x = 100, y = 140, color = "red", label = "Agriculture: 0.51035*x + 1.93603")+
  annotate("text", x = 100, y = 130, color = "blue", label = "Industrial: 1.13009*x - 26.80662")+
  annotate("text", x = 100, y = 120, color = "forestgreen", label = "Meat: 0.37534*x + 9.4808")+
  annotate("text", x = 100, y = 110, color = "purple", label = "Aggregate Marginal Cost: 0.18*x + 0.97")+
  annotate("text", x = 100, y = 100, color = "orange", label = "Agg. MC & Ecosystem Services: 0.18*x + 0.97 + 10")+
  theme_bw()+
  labs(
    y = "Marginal Cost of Abatement ($/AF)",
    x = "Reduction in Water Use (AF)",
    title = "Marginal Cost Curves in Baja California"
  )+
  geom_hline(aes(yintercept = 0))+
  geom_vline(aes(xintercept = 0))+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0, 150)+
  xlim(0, 350)
  
```

